Omics-based Single Step Trait Prediction

### 2017-09-14 paper/manuscript.tex
paper, add experiment id to trait table

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\centering
\caption{Acronyms for the trait names}
\label{table:TraitKey}
\begin{tabular}{@{}lll@{}}
\toprule
Trait              & Abbreviation & Data Set  \\ \midrule
Cob weight         & CW           & Diversity \\
Days to silking    & DS           & Diversity \\
Ear diameter       & ED           & Diversity \\
100-grain weight   & GW           & Diversity \\
Kernel width       & KW           & Diversity \\
Plant height       & PH           & Diversity \\
Dry matter yield   & DMY          & Hybrid    \\
Dry matter content & DMC          & Hybrid    \\
Lignin             & ADL          & Hybrid    \\
Fat                & FAT          & Hybrid    \\
Protein            & PRO          & Hybrid    \\
Starch             & STA          & Hybrid    \\
Sugar              & SUG          & Hybrid    \\ \bottomrule
\end{tabular}
\end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\centering
\caption{Acronyms for the trait names}
\label{table:TraitKey}
\begin{tabular}{@{}lll@{}}
\toprule
Trait              & Abbreviation & Data Set  & Experiment\\ \midrule
Cob weight         & CW           & Diversity & Exp1 \\
Days to silking    & DS           & Diversity & Exp1 \\
Ear diameter       & ED           & Diversity & Exp1 \\
100-grain weight   & GW           & Diversity & Exp1 \\
Kernel width       & KW           & Diversity & Exp1 \\
Plant height       & PH           & Diversity & Exp1 \\
Dry matter yield   & DMY          & Hybrid    & Exp2 \\
Dry matter content & DMC          & Hybrid    & Exp2 \\
Lignin             & ADL          & Hybrid    & Exp2 \\
Fat                & FAT          & Hybrid    & Exp2 \\
Protein            & PRO          & Hybrid    & Exp2 \\
Starch             & STA          & Hybrid    & Exp2 \\
Sugar              & SUG          & Hybrid    & Exp2 \\ \bottomrule
\end{tabular}
\end{table}
